Verifying Spatial Properties of Array Computations

### 2017-04-13 oopsla17/oopsla17.tex
more work on the model and more results

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}(sketch)
%  Any sublattice of a distributive lattice is a distributive lattice. Power sets
%  partially ordered with subset relation are distributive lattices. \region{N}
%  is a subset of $\mathcal{P}{(\bz{})^N}$ since all interval schemes are
%  subsets of this power set and; union and intersection cannot add an element
%  that is not already in the powerset. The inductive definition ensures that
%  \region{N} is closed under these operations. Therefore, \region{N} is a
%  distributive sublattice of $(\mathcal{P}{(\bz{})^N}, \subseteq)$.
\end{proof}

@@

>>>>

\begin{restatable}{prop}{regionLattice}
  \label{prop:regionLattice}
  $(\region{N},\cup,\cap,\subseteq)$ is a bounded distributive lattice with top
  $\top = \bz{}^N$ and bottom $\bot = \emptyset$.
\end{restatable}
%
\begin{proof}
  Straightforward, since $\cup$ and $\cap$ are on sets (and therefore commutative,
  associative, and absorptive with each
  other). Furthermore, $\mathbb{Z}^N \cap R = R$ and $\empty \cup R =
  R$ giving the bounds. Furthermore, the lattice is distributive since
 union distributes over intersection and vice versa
\end{proof}

\begin{defn}{}
  $\mathsf{Mult}$ and $\mathsf{Approx}$ are parametric labelled variant types
  with injections given by their definition:
%
  \begin{align*}
    \mathsf{Mult} \;\; a \;\; &
      \triangleq \mathsf{mult} \; a \;\mid\; \mathsf{only} \; a \\
    \mathsf{Approx} \;\; a \;\; &
      \triangleq \mathsf{exact} \; a \;\mid\; \mathsf{lower} \; a \;\mid\;
        \mathsf{upper} \; a
  \end{align*}
%
  \eg{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \to \mathsf{Approx}
  \; a$ etc.
  These will be used in the following subsection to give meaning to the
  specification modifiers for approximation and multiplicity.
\end{defn}

@@

\noindent
An interpretation function $\interp{-}_N$ provides a semantics to
specifications as a member of $\textsf{Mult} (\textsf{Approx} (\mathcal{P}{\bz}^N)))$
(where $n$ is the maximum dimensionality of the specification being
modelled) mapping closed\footnote{That is, we assume there are no
  occurrences of \textit{rvar} in a specification being modelled.  Any
  \emph{open} specification containing region variables can be made
  closed by straightforward syntactic substitution with a (closed)
  \textit{region}.} specifications to sets of
$n$-dimensional index schemes. The interpretation is overloaded on
\emph{regions} in \Cref{fig:region-model} and on the top-level
of a specification \textit{spec} in \Cref{fig:spatial-model}.
Various intermediate notions are used.
